Stack Safety as a Security Property

### 2020-07-09 main.tex
Abstract nit

We propose a formal definition of stack safety phrased in the technical
terminology of language-based security---as a combination of a
confidentiality property (callees should not be able to read their caller's
stack frames) and an integrity property (callees should not corrupt their
caller's stack frames or control state).
  %
We show how these properties are enforced or approximated by a range of
existing stack protection mechanisms\bcp{that is not exactly what we do,
  though.  Let's (re)write the contributions first.} and discuss some useful
stronger and weaker variants.  \bcp{should we mention stktokens here?}
\end{abstract}

>>>>

We propose a formal definition of stack safety phrased in the technical
terminology of language-based security---as a combination of a
confidentiality property (callees should not be able to read their caller's
stack frames) and an integrity property (callees should not corrupt their
caller's stack frames or control state).
  %
We discuss how these properties are enforced or approximated by  
existing stack protection mechanisms and describe some useful
provably stronger and weaker variants.  \bcp{should we mention stktokens here?}
\end{abstract}
